Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-05-23 edubots_surveys.Rnw
Update SoA and intro

% TODO: introduction
Introduction of new technologies in the classroom needs a combination of teacher education, as well as student willingness and skills. Some technologies are readily adapted, some of them take a long time to be adopted. In most cases, success or failure of the introduction of a

A \textit{chatbot} is a program that allows a computer to communicate in a similar way as a human does \cite{Gong2008}. Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker’s question fluently, and even ask other questions to the human.

The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}. These automatic systems ease personalized learning, adapting individuals' pace of learning, who get personalized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.

@@

% Maybe move it to a different place later
As a starting point, we have analyzed the responses to a survey from XXX teachers asking about their attitudes towards the use of chatbots in their classes. We are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? }
\item{ RQ2 -  Which kind of chatbots would teachers find useful in their classes?? }

>>>>

% TODO: introduction
The introduction of new technologies in the classroom needs a combination of teacher education, student willingness and (possibly new) skills in both. Some technologies are readily adapted, some of them take a long time to be adopted. In most cases, success or failure of the introduction of a new technology impinges on the colaboration of all the implied parties, which is why evaluating attitudes towards them is an essential first step.

In the framework of the Edubots KA2 European projects, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms. A \textit{chatbot} is a program that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language. Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker’s question fluently, and even ask other questions to the human.

The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, adapting individuals' pace of learning, who get personalized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.

@@

Chatbots are obviously associated to messaging applications, and in particular, direct messaging applications, since they are the only time of applications that are able to support a synchronous conversation betweeh the two parties. This is why in many cases chatbots couple messaging and the chatbot technology itself \cite{differ.chat}, while in others, you can create chatbots in any number of technologies and then attach them to a messaging application using their API.

% Maybe move it to a different place later
As a starting point, we have analyzed the responses to a survey from 300 teachers asking about their attitudes towards the use of chatbots in their classes. We are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 -  Which kind of chatbots would teachers find useful in their classes?? }
